Create data sets for modeling

### 2016-07-27 portfolio/analysis/3-createData_linear_modeling.Rmd
added lookup table for species percentages by strategy
largely for interpretation

topstrategies = group_by(cfecnew, p_holder, year) %>%
  summarize(strategy = paste(sort(unique(p_spec)), collapse = ", ")) %>%
  as_data_frame()
rev(sort(table(topstrategies$strategy)))[1:50]
cfecnew = left_join(cfecnew, topstrategies) # adds strategy column

@@

write.csv(rev(sort(table(topstrategies$strategy))), file = "../data-generated/strategies.csv")
```

>>>>

topstrategies = group_by(cfecnew, p_holder, year) %>%
  summarize(strategy = paste(sort(unique(p_spec)), collapse = ", ")) %>%
  as_data_frame()
rev(sort(table(topstrategies$strategy)))[1:50]
cfecnew = left_join(cfecnew, topstrategies) # adds strategy column
write.csv(rev(sort(table(topstrategies$strategy))), file = "../data-generated/strategies.csv")

@@

# Summarize key species landings by strategy.permit -- this is for interpretation later
key.spec = c("SOCK","COHO","CHUM","PINK","CHNK","PCOD","PHLB","SABL","TCRB","KCRB","DCRB","PLCK","SAC","POUND")
species_by_strategy = group_by(cfecnew, strategy.permit, spec) %>%
  summarize(earn.bySpec = sum(g_earn)) %>% 
  data.frame %>% 
  group_by(strategy.permit) %>% 
  mutate(totEarn = sum(earn.bySpec)) %>% 
  filter(spec %in% key.spec)
species_by_strategy$earn.bySpec = species_by_strategy$earn.bySpec/species_by_strategy$totEarn
species_by_strategy = filter(species_by_strategy, earn.bySpec > 0.1) %>% select(-totEarn)
# convert to wide format
library(reshape2)
melted_sbs <- melt(species_by_strategy, id.vars = c("strategy.permit", "spec"))
species_by_strategy <- dcast(melted_sbs, strategy.permit ~ spec + variable)
write.csv(species_by_strategy, file = "../data-generated/species_by_strategy.csv")
